---
title: "Mixomics TGIP sRNA and mRNA"
author: "Seth Barribeau"
date: "2021-07-16"
output: rmarkdown::html_document
liftr:
  maintainer: "Seth Barribeau"
  email: "seth.barribeau@gmail.com"
  from: "rocker/verse3.6.1"
  pandoc: true
  texlive: false
  sysdeps:
    - gfortran
  cran:
    - edgeR
    - pacman
    - igraph
  bioc:
    - mixOmics/6.16.3
#  remotes:
#    - "nanxstats/liftr"
#  include: "DockerfileSnippet"
---

To make dockerfile. Do not run unless you need to make a new docker image.
```{r test liftr}
# pacman::p_load("here", 'liftr')
# input=paste0(here(), '/tgipmixomicsb.Rmd')
# lift(input)
```

Based on [THIS TUTORIAL](http://mixomics.org/mixdiablo/case-study-tcga/) in Diablo.

Used [liftr](https://liftr.me/articles/liftr-intro.html) to produce a Docker file for these analyses.

```{r loadPackages}
pacman::p_load("here", "tidyverse", 'ggplot2', 'edgeR', 'BiocManager', 'igraph', 'mixOmics')

# if packages needed aren't there, install manually below.
# install.packages(c( 'pacman',"tidyverse", "here", "ggplot2", "edgeR", "liftr", "workflowr",'BiocManager'), dependencies = TRUE, INSTALL_opts = '--no-lock')
# BiocManager::install('mixOmics',INSTALL_opts = '--no-lock', force =TRUE)
# 
# library(ggplot2)
# library(mixOmics)
# library(edgeR)
# library(here)
```

```{r loadData}
df = read.csv(here('data', 'mRNA_miRNA_sRNA_noZero_TABLE2020.tsv'), sep='\t', header=T)
matTreat = c(rep('Primed',9), rep('Unprimed', 9))
dauTreat = rep(c(rep('G+', 3), rep('G-', 3), rep('Naive', 3)), 2)
colTreat = rep(c('1', '2', '3'), 6)
combTreat = paste(matTreat, dauTreat, sep='_')
```


Tidy up the dataframe

```{r dfCleanup}
`%!in%` <- Negate(`%in%`)

# this function takes a df with 'Geneid' as identifier. subsets duplicates into one df then sums the same id values. Keeps the non duplicated samples sep. Returns a list of df's one duplicates one nondup. 
dropDupes=function(indf){
  `%!in%` <- Negate(`%in%`)                             # opposite of %in%
  map=data.frame(Geneid=indf$Geneid, type = indf$type)  # get type and id separated.
  dupes = indf[duplicated(indf$Geneid),]                # get only the duplicated rows
  idDupes = unique(dupes$Geneid)                        # get only the id's of duplicates
  notdupes = indf[indf$Geneid %!in% idDupes,]           # df of non duplicated
  print('Number of duplicates')         
  print(length(idDupes))                                # number of duplicates
  print('Number of non duplicates')
  print(length(notdupes$Geneid))                        # number not duplicated
  newdf = data.frame()
  cnt = 1
  for(id in idDupes){                                   # loop through id's of duplicated geneids
    dupSum = colSums(dupes[dupes$Geneid %in%id,2:19])   # get sum of each matching row for each condition
    # dupSum = cbind(dupSum, dupes$type)                # add to new df
    # print(dupSum)
    newdf = rbind(newdf, dupSum)
    newdf$Geneid[cnt] = id
    newdf$type[cnt] = dupes$type[cnt]
    cnt = cnt+1 # try and add gene id to the rows
  }
  colnames(newdf)[1:18] = colnames(indf[2:19])          # rename headers to match input file [linked to this partic. format]
  duplicates = newdf # !!cbind(Geneid=idDupes, newdf)   # add geneids
  # duplicates = merge(duplicates, map, by='Geneid')    # merge with id's and type of nucl
  duplicates = duplicates[,c(19,1:18,20)]               # reorder so matches not dupe

  data = list(duplicates = duplicates,                  # make list of dfs
              notduplicates = notdupes[,1:20])
              # rawdupfile=newdf)
  return(data)
}

# miRNA = df[df$type=='miRNA',]
# x=dropDupes(miRNA)

test = dropDupes(df)
df_nodupes = rbind(test$duplicates, test$notduplicates)

nodupeOnly = test$notduplicates
dupeOnly = test$duplicates

mRNA = df_nodupes[df_nodupes$type=='mRNA',1:19] # drop tots and type
miRNA = df_nodupes[df_nodupes$type=='miRNA',1:19]
sRNA = df_nodupes[df_nodupes$type=='sRNA',1:19]
```

Normalize the individual data subsets (mRNA, miRNNA, sRNA) using edgeR. Since the miRNA and sRNA are sequenced in same libraries I'm normalizing together

```{r edgeRNorm}
misRNA =rbind(miRNA, sRNA)
qmRNA<-mRNA
qsmall<-misRNA
row.names(qmRNA)<-qmRNA$Geneid
row.names(qsmall)<-qsmall$Geneid 

dgListm <- DGEList(counts=qmRNA[,2:19], genes=rownames(qmRNA))
dgLists <- DGEList(counts=qsmall[,2:19], genes=rownames(qsmall))

countsPerMillion_m <- cpm(dgListm)
countsPerMillion_s <- cpm(dgLists)
# summary(countsPerMillion_m)
# summary(countsPerMillion_s)

countCheck_m <- countsPerMillion_m > 1
countCheck_s <- countsPerMillion_s > 1
# head(countCheck_m)
# head(countCheck_s)
keep_m <- which(rowSums(countCheck_m) >= 9) # half of samples
keep_s <- which(rowSums(countCheck_s) >= 9)

dgListm <- dgListm[keep_m,]
dgLists <- dgLists[keep_s,]

# summary(cpm(dgListm)) #
# summary(cpm(dgLists)) #
# dim(countsPerMillion_m) # 9670
# length(keep_m) # 8369
# dim(countsPerMillion_s) # 14495
# length(keep_s) # 4222

reducedCPM_m = countsPerMillion_m[keep_m,]
reducedCPM_s = countsPerMillion_s[keep_s,]
```

Need to split again into miRNA and sRNA

```{r splitSmall}
workings=reducedCPM_s
wkgmi = subset(workings, row.names(workings) %in% miRNA$Geneid )
wkgsi = subset(workings,   row.names(workings)%in%sRNA$Geneid)

```
Transpose dfs for mixomics. The df produced after cpm norm have rownames already set to gene names. Uncomment out lines if those are in a Geneid column as in counts file

```{r transp}
renameT=function(indf){
  # newdf = dropDupes(indf)
  newdf=indf
  #  row.names(newdf) = newdf$Geneid 
   # newdf=newdf[,-1] # drop gene name
  newdf = t(newdf)
  return(newdf)
}



mRNA_T=renameT(reducedCPM_m)
miRNA_T=renameT(wkgmi) 
# miRNA_T=renameT(miRNAnd) #no dupes only
# miRNA_Td=renameT(miRNAdup) #no dupes only
sRNA_T=renameT(wkgsi)

dim(reducedCPM_m); dim(wkgmi);dim(wkgsi)
# dim(mRNA_T);dim(miRNA_T);dim(sRNA_T)

# make list format for diablo
data = list(mRNA = mRNA_T, 
            miRNA = miRNA_T, 
            sRNA = sRNA_T)

# save reformatted df for use again if needed
write.csv(mRNA, here('output', 'mRNA_mixomics.csv'), row.names = F)#C:\Users\Seth\Box Sync\_mixomics\mixomics.Rmd
write.csv(miRNA, here('output', 'miRNA_mixomics.csv'), row.names = F)#C:\Users\Seth\Box Sync\_mixomics\mixomics.Rmd
write.csv(sRNA, here('output', 'sRNA_mixomics.csv'), row.names = F)#C:\Users\Seth\Box Sync\_mixomics\mixomics.Rmd

Y = combTreat # not sure I want the combo treatment here
data2 = data
data2$Y = Y
save(data, file=here('output', 'data_mixomics.RData'))
save(data2, file=here('output', 'data_mixomics_with_Y.RData'))
# load(here('output', 'data_mixomics.RData')) # to continue from this checkpoint
# load(here('output', 'data_mixomics_with_Y.RData'))

# check dimension
# lapply(data, dim)
# lapply(data, length)
# summary(Y)

```


Run PCA
```{r}
col = c('slategrey', 'darkorchid', 'cornflowerblue', 'black', 'firebrick4', 'turquoise4')


MyResult.pca <- pca(cbind(data$mRNA, data$miRNA, data$sRNA))  # 1 Run the method
plotIndiv(MyResult.pca, group =  Y, groupcol.per.group=col) # 2 Plot the samples no coloring, how to do sep?
```

```{r getCorr}
sgccda.res = block.splsda(X = data, Y = data2$Y, ncomp = 3) 
plotDiablo(sgccda.res, ncomp=3) # get correlations ; highly corr
```

Specify the design correlation matrix from above. V. High correlation. Sticking with the highly correlated values will select more of the strongly correlated features (high in mRNA and miRNA for eg). These are not necessarily the most discriminatory. Using smaller correlation value will create better discrimination (unsupervised clustering)

```{r highCorrDesign}
design = matrix(c(0,0.88,0.94,0.88,0,0.96,0.94,0.96,0), ncol = length(data), nrow = length(data), 
                 dimnames = list(names(data), names(data)))
design
```

Do the same for lower correlation for clustering
```{r lowCorrDesign}
design2 = matrix(0.1, ncol = length(data),  nrow = length(data), #length(data), 
                dimnames = list(names(data), names(data)))
diag(design2) = 0

design2

```


```{r component no}
set.seed(123) # for reproducibility
sgccda.res = block.splsda(X = data, Y = Y, ncomp = 6, design = design)
sgccda.res2 = block.splsda(X = data, Y = Y, ncomp = 6, design = design2)

# this code takes a couple of min to run
perf.diablo = perf(sgccda.res, validation = 'Mfold', folds = 3, nrepeat = 10) 
perf.diablo2 = perf(sgccda.res2, validation = 'Mfold', folds = 3, nrepeat = 10)

# #perf.diablo  # lists the different outputs
# plot(perf.diablo) 
# plot(perf.diablo2)
# 
# perf.diablo$choice.ncomp$WeightedVote
# ncomp = perf.diablo$choice.ncomp$WeightedVote["Overall.BER", "centroids.dist"]
```

The perf.diablo above shows the error rate according to the number of components included in the analysis. Doesn't seem to alter much, so not v. descriptive. 

```{r keepx}

test.keepX_lots = list (mRNA = c(5:50), # 
                   miRNA =c(5:50),
                   sRNA = c(5:50))

test.keepX_few = list (mRNA = c(5:9, seq(10,49,5)), # 
                   miRNA =c(5:9, seq(10,49,5)),
                   sRNA = c(5:9, seq(10,49,5)))


# BPPARAM <- BiocParallel::MulticoreParam(workers = parallel::detectCores()-1) # DOESN'T WORK ON WINDOWS.
BPPARAM <- BiocParallel::SnowParam(workers = parallel::detectCores()-1)

# tune.TCGA_lots_lowCorr = tune.block.splsda(X = data, Y = Y, ncomp = 5, 
#  takes a very long time
#                              test.keepX = test.keepX_lots, design = design,
#                              validation = 'Mfold', folds = 3, nrepeat = 1, 
#                              BPPARAM = BPPARAM, 
#                              dist = "centroids.dist")

# tune.TCGA_lots_highCorr = tune.block.splsda(X = data, Y = Y, ncomp = 5, 
                              # test.keepX = test.keepX_lots, design = design2,
                              # validation = 'Mfold', folds = 3, nrepeat = 1, 
                              # BPPARAM = BPPARAM, 
                              # dist = "centroids.dist")

tune.TCGA_few_lowCorr = tune.block.splsda(X = data, Y = Y, ncomp = 5, 
                              test.keepX = test.keepX_few, design = design2,
                              validation = 'Mfold', folds = 3, nrepeat = 1, # increasing nrepeat should improve confidence
                              BPPARAM = BPPARAM, 
                              dist = "centroids.dist")


tune.TCGA_few_highCorr = tune.block.splsda(X = data, Y = Y, ncomp = 5, 
                              test.keepX = test.keepX_few, design = design,
                              validation = 'Mfold', folds = 3, nrepeat = 1, 
                              BPPARAM = BPPARAM, 
                              dist = "centroids.dist")
```

```{r keeps}
# list.keepX_lots_lowCorr = tune.TCGA_lots_lowCorr$choice.keepX
# list.keepX_lots_highCorr = tune.TCGA_lots_highCorr$choice.keepX
list.keepX_few_lowCorr = tune.TCGA_few_lowCorr$choice.keepX
list.keepX_few_highCorr = tune.TCGA_few_highCorr$choice.keepX
#####
# list.keepX_lots_lowCorr

MyResult.diabloLC <- block.splsda(X=data, Y=Y, ncomp=6, keepX=list.keepX_few_lowCorr, design= design2)
perf.diablo = perf(MyResult.diabloLC, validation = 'loo', BPPARAM=BPPARAM)
plot(perf.diablo, col = color.mixo(5:7), sd = TRUE, legend.position = 'horizontal')
#  

MyResult.diabloHC <- block.splsda(X=data, Y=Y, ncomp=6, keepX=list.keepX_few_highCorr, design= design)
perf.diablo = perf(MyResult.diabloHC, validation = 'loo', BPPARAM=BPPARAM)
plot(perf.diablo, col = color.mixo(5:7), sd = TRUE, legend.position = 'horizontal')


sgccda.resLC = block.splsda(X = data, Y = Y, ncomp = 5, 
                          keepX = list.keepX_few_lowCorr, design = design2)
# sgccda.resLC   # list the different functions of interest related to that object

sgccda.resLC$design

# mrna variables selected on component 1 ... 
selectVar(sgccda.resLC, block = 'mRNA', comp = 1)$mRNA$name  
selectVar(sgccda.resLC, block = 'miRNA', comp = 1)$miRNA$name
selectVar(sgccda.resLC, block = 'sRNA', comp = 1)$sRNA$name 

sgccda.resHC = block.splsda(X = data, Y = Y, ncomp = 5, 
                          keepX = list.keepX_few_highCorr, design = design)
# sgccda.resHC   # 
sgccda.resHC$design

# mrna variables selected on component 1 ... 
selectVar(sgccda.resHC, block = 'mRNA', comp = 1)$mRNA$name  # 
selectVar(sgccda.resHC, block = 'miRNA', comp = 1)$miRNA$name 
selectVar(sgccda.resHC, block = 'sRNA', comp = 1)$sRNA$name 
```

Produce PCA plots of 
```{r PCA}
dateStr = Sys.Date()

col = c('slategrey', 'darkorchid', 'cornflowerblue', 'black', 'firebrick4', 'turquoise4')

pdLC = plotDiablo(sgccda.resLC, ncomp =1, col.per.group = col)
pdHC = plotDiablo(sgccda.resHC, ncomp =1, col.per.group = col)
# pd

piLC = plotIndiv(sgccda.resLC, guide = FALSE, legend = TRUE, title = 'DIABLO', col.per.group = col) # 
ggsave(here('output', "plotIndiv130821_lowCor.pdf"))

piHC = plotIndiv(sgccda.resHC, guide = FALSE, legend = TRUE, title = 'DIABLO', col.per.group = col) # 
ggsave(here('output', "plotIndiv130821_highCor.pdf"))


paLC = plotArrow(sgccda.resLC, ind.names = TRUE , col.per.group = col, legend.title = 'Treatment', pch.size=3, title = 'DIABLO') # 
paLC

ggsave(here('output', paste0("plotArrows", dateStr, "_lowCor.pdf")))
ggsave(here('output', paste0("plotArrows", dateStr, "_lowCor.png")))



paHC = plotArrow(sgccda.resHC, ind.names = TRUE , col.per.group = col, legend.title = 'Treatment', pch.size=3, title = 'DIABLO') # 
paHC


ggsave(here('output', paste0("plotArrows", dateStr, "_highCor.pdf")))
ggsave(here('output', paste0("plotArrows", dateStr, "_highCor.png")))
```



```{r variablePlots}
cicLC<-plotVar(sgccda.resLC, var.names = FALSE, style = 'graphics', legend = TRUE,  # Fewer now
        pch = c(16, 17, 15), cex = c(2,2,2), col = c('darkorchid', 'brown1', 'lightgreen'))
cicHC<-plotVar(sgccda.resHC, var.names = FALSE, style = 'graphics', legend = TRUE,  # Fewer now
        pch = c(16, 17, 15), cex = c(2,2,2), col = c('darkorchid', 'brown1', 'lightgreen'))
```

# Circos connections

Show correlations among mRNA/miRNA/sRNA at 0.8 correlation threshold and get table output of correlations. These need to be run in the console on my version of Rstudio on Windows.

```{r circos}

cutoff = 0.8
pdf(here('output', paste0("Circos", '_', cutoff, '_', dateStr, '_lowCor.pdf')))
circosPlot(sgccda.resLC, cutoff = cutoff, line = TRUE, 
           color.blocks= c('darkorchid', 'brown1', 'lightgreen'),
           comp = 1:2,
           color.cor = c("chocolate3","grey20"), size.labels = 1.5, color.Y = col) # variables=0.35, 
dev.off()

pdf(file=here('output', paste0("Circos", '_', cutoff, '_',  dateStr, '_highCor.pdf')))
circosPlot(sgccda.resHC, cutoff = cutoff, line = TRUE, 
           comp = 1:2,
           color.blocks= c('darkorchid', 'brown1', 'lightgreen'),
           color.cor = c("chocolate3","grey20"), size.labels = 1.5, color.Y = col)  
dev.off()


cLC = circosPlot(sgccda.resLC, cutoff = cutoff, line = TRUE, # works but hard to tell
           comp = 1:2,
           color.blocks= c('darkorchid', 'brown1', 'lightgreen'),
           color.cor = c("chocolate3","grey20"), size.labels = 1.5, color.Y = col) # variables=0.35, 
cHC = circosPlot(sgccda.resHC, cutoff = cutoff, line = TRUE, 
           comp = 1:2,
           color.blocks= c('darkorchid', 'brown1', 'lightgreen'),
           color.cor = c("chocolate3","grey20"), size.labels = 1.5, color.Y = col) # variables=0.35, 


write.csv(cLC, here('output',  paste0("Circos", cutoff dateStr, '_lowCor.csv')), row.names = TRUE)
write.csv(cHC, here('output',  paste0("Circos", '_', cutoff, '_', dateStr,'_highCor.csv')), row.names = TRUE)

```

Save RData file up to now.

```{r, save}
# save .Rda file
save(sgccda.resLC, file = here("output", paste0("sgccda.res_", dateStr, '_lowCor.Rda')))
save(sgccda.resHC, file = here("output", paste0("sgccda.res_", dateStr, '_highCor.Rda')))
# load(here("output", "sgccda.res_0.1Corr_largeRandom_130821.Rda"))
```

Create network plots. Purple circles are mRNA, red squares miRNA, greenish squares sRNA. Needs to be run in console on my windows version of Rstudio.

```{r network}
dev.off()

pdf(here('output',paste0('networkPlot_', cutoff, '_', dateStr, '_lowCor.pdf')))
network(sgccda.resLC, blocks = c(1,2,3), # doesnt work in rstudio. save as image w save and name.save
        color.node = c('darkorchid', 'brown1', 'lightgreen'), 
        shape.node = c('circle', 'rectangle', 'rectangle'),
        cutoff = cutoff, show.color.key = TRUE, 
        color.edge =  color.jet(100) #,
        # interactive = TRUE
        )
legend('bottomright', legend=c('mRNA', 'miRNA', 'sRNA'), pch=(c(19,15,15)), col=c('darkorchid', 'brown1', 'lightgreen'),  y.intersp=1, x.intersp=1, xpd=TRUE, bty="n")#, x=0, y=-2.5)
# note, size of dot is just linked to name length
dev.off()

pdf(here('output',paste0('networkPlot_', cutoff, '_', dateStr, '_highCor.pdf')))
network(sgccda.resHC, blocks = c(1,2,3), # doesnt work in rstudio. save as image w save and name.save
        color.node = c('darkorchid', 'brown1', 'lightgreen'), 
        shape.node = c('circle', 'rectangle', 'rectangle'),
        cutoff = 0.8, show.color.key = TRUE, 
        color.edge =  color.jet(100) #,
        # interactive = TRUE
        )
legend('bottomright', legend=c('mRNA', 'miRNA', 'sRNA'), pch=(c(19,15,15)), col=c('darkorchid', 'brown1', 'lightgreen'),  y.intersp=1, x.intersp=1, xpd=TRUE, bty="n")#, x=0, y=-2.5)
# note, size of dot is just linked to name length
dev.off()
```
The network can be saved in a .gml format to be input into the software Cytoscape, using the R package igraph

```{r savenetw}
# library(igraph)
my.networkLC = network(sgccda.resLC, blocks = c(1,2,3),
        color.node = c('darkorchid', 'brown1', 'lightgreen'), 
        shape.node = c('circle', 'rectangle', 'rectangle'),
        color.edge =  color.jet(100), #,
        cutoff = cutoff)
write.graph(my.networkLC$gR, file = here("output", paste0("myNetwork_", cutoff, '_', dateStr,"lowCor.gml")), format = "gml")

my.networkHC = network(sgccda.resHC, blocks = c(1,2,3),
        color.node = c('darkorchid', 'brown1', 'lightgreen'), 
        shape.node = c('circle', 'rectangle', 'rectangle'),
        color.edge =  color.jet(100), #,
        cutoff = cutoff)
write.graph(my.networkHC$gR, file = here("output", paste0("myNetwork_", cutoff, '_', dateStr, "highCor.gml")), format = "gml")

```

Save correlation matrix > cutoff value

```{r networkgenes}
# head(my.networkLC$M_mRNA_miRNA)
# head(my.network$M_mRNA_sRNA)
# head(my.network$M_miRNA_sRNA)

write.table(my.networkLC$M_mRNA_miRNA, 
            file=here('output', paste0("networkDF_mRNA_miRNA_lowCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)
write.table(my.networkLC$M_mRNA_sRNA, 
            file=here('output', paste0("networkDF_mRNA_sRNA_lowCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)
write.table(my.networkLC$M_miRNA_sRNA, 
            file=here('output', paste0("networkDF_miRNA_sRNA_lowCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)

write.table(my.networkHC$M_mRNA_miRNA, 
            file=here('output', paste0("networkDF_mRNA_miRNA_highCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)
write.table(my.networkHC$M_mRNA_sRNA, 
            file=here('output', paste0("networkDF_mRNA_sRNA_highCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)
write.table(my.networkHC$M_miRNA_sRNA, 
            file=here('output', paste0("networkDF_miRNA_sRNA_highCor_", cutoff, '_', dateStr, ".csv")),
            sep=';',quote=FALSE, row.names=TRUE)
```

```{r getLoadingPlot}
dev.off()

pdf(here('output', paste0('Loadings_lowCor_', cutoff, '_', dateStr, '.pdf')))
plotLoadings(sgccda.resLC, comp = 1, contrib = 'max', method = 'median', legend.color = col, legend.title = "Treatment", width =10, height=12)
plotLoadings(sgccda.resLC, comp = 2, contrib = 'max', method = 'median', legend.color = col, legend.title = "Treatment")
dev.off()


pdf(here('output', paste0('Loadings_highCor_', cutoff, '_', dateStr, '.pdf')))
plotLoadings(sgccda.resHC, comp = 1, contrib = 'max', method = 'median', legend.color = col, legend.title = "Treatment")
plotLoadings(sgccda.resHC, comp = 2, contrib = 'max', method = 'median', legend.color = col, legend.title = "Treatment")
dev.off()



loadints1LC=plotLoadings(sgccda.resLC, comp = 1, contrib = 'max', method = 'median', plot=FALSE)
loadints2LC=plotLoadings(sgccda.resLC, comp = 2, contrib = 'max', method = 'median', plot=FALSE)

loadints1HC=plotLoadings(sgccda.resHC, comp = 1, contrib = 'max', method = 'median', plot=FALSE)
loadints2HC=plotLoadings(sgccda.resHC, comp = 2, contrib = 'max', method = 'median', plot=FALSE)
```


Produce heatmaps of genes and save the ouputs of gene matrices. To adjust plot dim to see all the genes, [install dev version of mixomics.](https://mixomics-users.discourse.group/t/cimdiablo-number-of-genes-on-the-x-axis/670/2) Likely will be fixed in future releases. The current version does produce the output tables that are in the order of
`BiocManager::install('aljabadi/mixOmics@cimdiablo-plotdims')`

`cimDiablo(sgccda.resLC, comp = c(1,2), save = "pdf", name.save="cimdiablo", save.width=12, save.height=8, margins = c(6, 15))`




```{r heatmapMulti}


pdf(here('output', paste0('heatmap_lowCor_', dateStr, '.pdf')))
cimDiablo(sgccda.resLC, color.Y=col, legend.position='right', size.legend = 0.85, margins = c(12, 15))# ,lwid = c(0,0.2,5))
dev.off()


xLC=cimDiablo(sgccda.resLC, color.Y=col, legend.position='right', size.legend = 0.85, margins = c(12, 15))# ,lwid = c(0,0.2,5))

save(xLC, file=here('output', paste0("heatmap_lowCor_", dateStr, ".Rda")))

pdf(here('output', paste0('heatmap_highCor_', dateStr, '.pdf')))
cimDiablo(sgccda.resHC, color.Y=col, legend.position='right', size.legend = 0.85, margins = c(12, 15))# ,lwid = c(0,0.2,5))
dev.off()

xHC=cimDiablo(sgccda.resHC, color.Y=col, legend.position='right', size.legend = 0.85, margins = c(12, 15))# ,lwid = c(0,0.2,5))

save(xHC, file=here('output', paste0('heatmap_highCor_', dateStr, '.Rda')))
```


```{r saveworkspace}
save.image(here('output', paste0("mixomicWorkspace_", dateStr, ".RData")))

```

